\documentclass{letter}
\signature{John de la Garza}

\makeatletter
\let\@texttop\relax
\makeatother

\begin{document}
\begin{letter}{}

I am interested in the position of Full Stack Software Engineer.  I
learned about your company while looking at a former
employee's (Bill Moorier) website after noticing some code he had
written for the Linux Kernel.

After further reading about the company and the position, I am confident
that I would enjoy being part of the team and could contribute.  I
have solid programming skills and have worked with Python, PostgreSQL,
and Django.

Computer programming is something that I really enjoy and get a lot
of satisfaction from.  I spend a lot of my time reading and writing code
and appreciate having my code seen and questioned by others.

A Linux environment is where I am most at home, although I have
done work with other Unix variants.  Python, C, and Scheme are my
favorite languages.  I have never used Scheme for more than a learning tool,
but have learned a lot about making programs easier to debug in other
languages by thinking about things from a functional point of view.

When it comes to full stack work, I have worked on projects where
I was responsible for the documentation, installation and
configuration of the OS, DNS, database server, schema, server side code,
web server, router/firewall, and even some front end JavaScript.

I am available to interview by phone or in person with short notice.  I
can be reached by phone at 657 400 9422.  Thank you for your time.

\closing{Sincerely yours,}
\end{letter}
\end{document}
