\documentclass{letter}
\signature{John de la Garza}

\makeatletter
\let\@texttop\relax
\makeatother

\begin{document}
\begin{letter}{}
\opening{Dear Sir or Madam:}

I am interested in the position of Full Stack Software Engineer.  I
learned about your company while looking at a former
employee's (Bill Moorier) website after noticing some code he had
written for the Linux Kernel.

I did some more research and got the idea that I may be a good
fit for the position.  I have strong python skills and have worked with
postgresql and Django.
I am someone who really enjoys programming and playing with computers in
general.  I am most comfortable in a Linux environment, although I have
done work with other Unix variants.  My favorite languages are Python,
C, and Scheme.  I have never used Scheme for more than a learning tool,
but have learned a lot about making programs easier to debug in other
languages by thinking about things from a functional point of view.

I would consider my self someone who has worked on the full stack.
I've worked on projects where I was responsible for the documentation,
installation and
configuration of the OS, DNS, database server, schema, server side code,
web server, router/firewall, and even some front end javascript.
When called upon to write front end or GUI code, I usually use default widgets
and colors expecting lots of feedback on asthetics issues.  This has not
been by strong suit.
I understand requirements change as the development process reveals
more insights.  I am ok with things changing.  I am also a big fan of
peer view and appreciate having my code seen by others and questioned.

I am available to interview by phone or in person with short notice.  I
can be reached by phone at 657 400 9422.  Thank you for your time.

\closing{Sincerely yours,}
\end{letter}
\end{document}
