\documentclass[12pt]{letter} % Default font size of the document, can use values of 10pt, 11pt or 12pt, but you may need to adjust margins if reducing font size

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{fouriernc} % Use the URW Schoolbook L font, similar to New Century Schoolbook

\usepackage{geometry} % Required for adjusting page dimensions and margins

\geometry{
	paper=a4paper, % Paper size, change to letterpaper for US letter size
	top=2cm, % Top margin
	bottom=2.5cm, % Bottom margin
	left=3.25cm, % Left margin
	right=3.25cm, % Right margin
	%showframe, % Uncomment to show how the type block is set on the page
}

\begin{document}

\begin{letter}{}

\begin{center}
	\large\bfseries % Font size and styling
	John de la Garza \\ % Your name
	Westminster, CA 92683 \\
	(714) 895-6311 \\
        john@jjdev.com
\end{center}

\vspace{1cm} % Vertical whitespace

\signature{John de la Garza} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	COVER LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear HR Team,}

I have always been curious and fascinated by computers.
As a child, I was drawn to computers partially due to graphics and
video games.  Later I became more interested in operating systems and
networking.  I have spent time writing low level code as
well as high level code in many languages.  While in school I was exposed
to relational databases and found them to be another interest of mine.

I am quite aware that the computer business is just that a business.
At my last job, I spent time profiling network and memory usage and
was able to make changes that had cost savings.  For example, after
changing some network code to use a different type of handshake on
the initial connection we lowered our AWS bill by \$20k/month.

Programming has been a passion of mine.  I have spent much time reading
books and reading lots of source code from successful projects and
unsuccessful projects as well.  I have come to realize that writing code
that avoids adding accidental complexities and ends with code that is
as simple as possible is key to making systems that can be maintained
and extended easily.  One of the biggest compliments I received was
'Reading your code is a joy', after giving my code to a new maintainer.
Along with programming I also enjoy building systems.  By this, I mean
creating things that involve many programs working together.

I would greatly appreciate the opportunity to meet with you and further
discuss my qualifications and your requirements in detail.  Thank you
for your consideration.


\closing{Sincerely,}

\end{letter}

\end{document}
