\documentclass{res}
\begin{document}
\name{John de la Garza}
\address{john@jjdev.com - (714) 895 6311 - Westminster, CA 92683}

\pagenumbering{arabic}
\begin{resume}
    Systems Engineer with a passion for programming, discovery, and
    problem solving.  I have worked on things from low-level code
    to distributed systems and everything in between.

    Over the last year I have started using AI tools more frequently
    for large parts of the software development process.  For
    example:  RFCs, specifications, test plans, implementation. As
    well as debugging and root cause analysis for issues that span
    many systems.

\section{SKILLS}
\begin{itemize}
  \item
    {\bf domain:} Linux, distributed systems, cloud infrastructure, backend
  \item
    {\bf language:} Python, Go, SQL, Rust, Bash, C, Perl, Lua, JavaScript, Ruby, Lisp
  \item
    {\bf technology:} AWS, Kubernetes, PostgreSQL, MySQL, Redis, Nginx,
    Flask, WebSockets, SQLAlchemy, Netbox, FastAPI, Prometheus, Grafana, Django
  \end{itemize}

\section{WORK EXPERIENCE}

  {\large \bf Cloudflare, remote, Systems Engineer \hfill 6/2024 to 5/2026}
  \begin{itemize}
  \item
    Owned and maintained the asset ingestion system that pulls asset
    data from vendor APIs and creates corresponding records in Netbox.
    Onboarded new vendors end-to-end: defining schemas and specs,
    coordinating with vendors on data format and delivery, and
    collaborating with cross-functional teams internally.
  \item
    Automated hardware vendor asset ingestion, replacing a manual
    spreadsheet-upload process so assets appeared in Netbox
    automatically, eliminating significant toil for the hardware team.
  \item
    Automated rack-integrator data ingestion to eliminate manual
    tracking and spreadsheet reconciliation for a complex multi-party
    asset hand-off flow.
  \item
    Built a self-service UI component in the Netbox plugin enabling users
    to create hardware part-number to model-number mappings, eliminating
    manual spreadsheet-based ticket workflows.
  \item
    Built a reconciliation system which kept our asset data source of truth
    synchronized with what the hardware was reporting.  Devices
    would run agents which would publish device state to a message
    bus.  Reconciler would subscribe to the bus and detect diffs between
    device-reported state and Netbox.  Updates would be made if the
    data was easy to update, otherwise a person would be notified.
  \item
    Wrote test coverage for all new code and refactored existing code in the
    Netbox plugin and asset ingestion system, reducing mocking overhead and
    improving test execution speed.
  \item
    Supported network engineers as part of a regular on-call rotation,
    troubleshooting provisioning issues with root cause analysis.
  \end{itemize}

  {\large \bf Blackberry, remote, Senior Software Engineer \hfill 4/2019 to 9/2023}
  \begin{itemize}
  \item
    Led design and development of a REST API backend for an enterprise
    security product, spanning feature work, bug fixes, deployments, and
    operations.  Development was done mostly in Go and Python.
  \item
    First responder for customer-facing incidents, tracking root causes
    across distributed services and deploying fixes.
  \item
    Frequently pair programmed with others that were newer to the job
    to get them up to speed on using git consistently and learning how
    to run/develop/debug the different microservices.
  \item
    Transitioned several services from Python to Go.
  \item
    Used OpenResty/Lua to build a bidirectional WebSocket gateway routing messages between customer devices, Kinesis streams, and internal HTTP microservices via pub/sub.
  \end{itemize}

  {\large \bf Comscore, Portland, OR, Senior Software Engineer \hfill 11/2016 to 12/2018}
  \begin{itemize}
  \item
    Worked on a distributed system that counted watched ads and determined
    who watched them, handling data ingestion, normalization, summarization,
    and export pipelines.
  \item
    Built composable command-line tools that acted as a query language for
    analyzing incoming data and generating custom reports.
  \end{itemize}

  {\large \bf Idealist.org, Portland, OR, Senior Developer \hfill 7/2015 to 7/2016}
  \begin{itemize}
    \item
    Worked on a team creating a REST API that needed
    to inter-operate with an existing model, database, and messaging
    system. It provided HTTPS endpoints to allow other systems to post
    jobs in an automated fashion.  This involved doing a deep dive into
    the code to fully understand the existing architecture.
    \item
    Created a new system that allowed
    customers to bulk post job listings.  It was available to the end users
    as a REST API where they could submit jobs, check status, etc.
    It was consistent, well-documented, and designed to be discoverable.
    \item
    Wrote shell scripts to create a chroot-based sandbox.  This provided
    a reproducible development environment on individual developer
    computers.
  \end{itemize}

\section{EDUCATION}
Cal State Fullerton, BA Management Information Systems, Dean's List

\section{SPOKEN LANGUAGES}
English and Spanish
\end{resume}
\end{document}
